Summer 2025 ToDo

### 2025-11-06 Relations/Paper/Formalization.tex
Typo

As outlined in the previous section, \texttt{Properties.agda}, \texttt{Seq.agda}, and \texttt{ClosureOperators.agda} define most standard termination and confluence properties. The file \texttt{Base.agda} introduces additional defitions which are required for the formalization of the propositions found in Chapter 1 of \terese.

>>>>

As outlined in the previous section, \texttt{Properties.agda}, \texttt{Seq.agda}, and \texttt{ClosureOperators.agda} define most standard termination and confluence properties. The file \texttt{Base.agda} introduces additional definitions which are required for the formalization of the propositions found in Chapter 1 of \terese.
